\documentclass[11pt,a4paper,unicode]{moderncv}

\moderncvtheme{classic}
\usepackage[utf8]{inputenc}

\usepackage[scale=.86]{geometry}          % smaller number -> text takes more space
\AtBeginDocument{\recomputelengths}

% Hyperlinks
\usepackage[unicode]{hyperref}                      % to use hyperlinks
\definecolor{linkcolour}{rgb}{0,0.2,0.6}            % hyperlinks setup
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Stephanie}
\familyname{Wang}
\address{University of California, San Diego}{Department of Computer Science and Engineering}
\email{evast@g.ucla.edu}


\nopagenumbers{}                    

\begin{document}
\maketitle

\section{Education}
%\cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
\cventry{2014-2020}{Ph.D. in Mathematics}{UCLA}{}{Dissertation advisor: Joseph Teran}
{}
\cventry{2014-2016}{M.S. in Mathematics}{UCLA}{}{}{}
\cventry{2009-2013}{B.S. in Mathematics}{National Taiwan University}{}{\textit{magna cum laude}}
{}


\section{Research Experience}
\cventry{2020-present}{Postdoc -- under Prof. Albert Chern}{UCSD}{}{San Diego, CA}{Weird maths, Houdini, and Python programming with applications in geometric processing, physics simulation, inverse rendering, and geometric learning.}
\cventry{2019-2020}{Ph.D. Study -- under Prof. Wilfrid Gangbo}{UCLA}{}{Los Angeles, CA}{Regularity theory for minimizers of polyconvex functionals related to Navier-Stokes equation. }
\cventry{2019 summer}{Summer Exchange -- under Prof. Johan Gaume}{EPFL}{}{Lausanne, Switzerland}
{Physics-based simulations, post-processing, and data analysis of snow and tire interaction and general consultation at the Snow and Avalanche Simulation Laboratory. }
\cventry{2016-2019}{Ph.D. Study -- under Prof. Joseph Teran}{UCLA}{}{Los Angeles, CA}
{Physics-based simulations for animation purposes using C++ programming, convex and nonconvex optimizations, numerical PDEs, numerical linear algebra, and multithreading. }
\cventry{2013-2014}{Research Assistantship -- under Prof. Wen-Wei Lin}{NCTU}{}{Hsinchu, Taiwan}{Generalized eigenvalue problems using MATLAB programming.}

\section{Industry Experience}
\cventry{2018 summer}{Technology Intern}{Walt Disney Animation Studio}{}{Burbank, CA}
{R\&D for pioneer simulation technology in animated feature film, teaming with FX artists, numerical analysis, continuum mechanics, C++, HDK.}

\section{Teaching Experience}
% \cventry{2020-present}{Postdoc}{UCSD Computer Science and Engineering}{}{San Diego, CA}{}
\cventry{2020}{Assistant Adjunct Professor}{UCLA Math Dept}{}{Los Angeles, CA (virtual)}
{Teaching Machine Learning (Math156) and Calculus of Several Variables (Math32A).}
\cventry{2019 spring}{Graduate Student Instructor}{UCLA Math Dept}{}{Los Angeles, CA}
{Teaching Linear Algebra and Applications (Math33A).}
\cventry{2015-2020}{Teaching Assistant}{UCLA Math Dept}{}{Los Angeles, CA}
{Leading discussion sessions and grading homework/exams for: linear algebra and intro to mathematical proofs, undergrad- and grad-level numerical methods, and C++ programming (introductory, intermediate, and advanced).}
% \cventry{2014 summer}{Course Organizer}{2014 Formosan Summer School on Logic, Language, and Computation}{}{}{}


\section{Awards and Prizes}
\cventry{Jul 2019}{Best Paper Award}{ACM SIGGRAPH/Eurographics Symposium on Computer Animation}{}{}{}
\cventry{Sep 2014}{Eugene V. Cota-Robles Fellowship}{UCLA}{}{}{}
\cventry{Jun 2013}{Dean's Award, College of Science}{National Taiwan University}{}{}{}
\cventry{Aug 2012}{Bronze Medal, Applied and Computational Mathematics}{S.T. Yau College Student Mathematics Contest}{}{}{}

\section{Preprints}
\nocite{*}
\bibliographystyle{plain}
\bibliography{preprints}
\cvline{Nov 2021}{D. Palmer, D. Smirnov, \textbf{S. Wang}, A. Chern, J. Solomon, DeepCurrents: Learning Implicit Representations of Shapes with Boundaries, \href{https://arxiv.org/abs/2111.09383}{arXiv}.}
\cvline{Aug 2019}{J. Carlen, J. Pont, C. Mentus, S. Chang, \textbf{S. Wang}, M. Porter, Role Detection in Bicycle-Sharing Networks Using Multilayer Stochastic Block Models, \href{https://arxiv.org/abs/1908.09440}{arXiv}.}

\section{Publications}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}
\cvline{Sep 2021}{L. Blatny, H. Löwe, \textbf{S. Wang}, J. Gaume, Computational micromechanics of porous brittle solids, Computers and Geotechnics, \href{https://www.sciencedirect.com/science/article/pii/S0266352X21002822}{ScienceDirect}.}
\cvline{Aug 2021}{\textbf{Stephanie Wang} and Albert Chern, Computing minimal surfaces with differential forms, ACM Transactions on Graphics (SIGGRAPH 2021), \href{https://dl.acm.org/doi/10.1145/3450626.3459781}{ACM Digital Library}.}
\cvline{Mar 2020}{\textbf{Stephanie Wang}, A Material Point Method for Elastoplasticity with Ductile Fracture and Frictional Contact, UCLA Doctoral Dissertation, \href{https://www.proquest.com/docview/2389768700?pq-origsite=gscholar&fromopenview=true}{ProQuest}.}
\cvline{Nov 2019}{M. Ding, X. Han, \textbf{S. Wang}, T. Gast, J. Teran, A thermomechanical material point method for baking and cooking, ACM Transactions on Graphics (SIGGRAPH Asia 2019), \href{https://dl.acm.org/doi/10.1145/3355089.3356537}{ACM Digital Library}.}
\cvline{Jul 2019}{X. Han, T. Gast, Q. Guo, \textbf{S. Wang}, C. Jiang, J. Teran, A Hybrid Material Point Method for Frictional Contact with Diverse Materials, Proc ACM on Computer Graphics and Interactive Techniques (SCA 2019), \href{https://dl.acm.org/doi/10.1145/3340258}{ACM Digital Library}. }
\cvline{Jul 2019}{\textbf{S. Wang}, M. Ding, T. Gast, L. Zhu, S. Gagniere, C. Jiang, J. Teran, Simulation and Visualization of Ductile Fracture with the Material Point Method, Proc ACM on Computer Graphics and Interactive Techniques (SCA 2019 Best Paper), \href{https://dl.acm.org/doi/10.1145/3340259}{ACM Digital Library}.}

\section{Invited talks}
% \cventry[spacing]{years}{degree/job title}{institution/employer}{localization}{optionnal: grade/...}{optional: comment/job description}
\subsection{Conferences and workshops}
\cventry{Sep 2021}{Geometry Workshop in Obergurgl}{}{Obergurgl, Austria (\textbf{in person})}{}{}
\cventry{Aug 2021}{SIGGRAPH}{}{(virtual)}{}{}
\cventry{Aug 2019}{SCA}{}{Los Angeles, CA}{}{}

\subsection{Seminars at research institutions}
\cventry{Feb 2022}{NCSU}{}{Raleigh, NC (virtual)}{}{}{} % Geometry and Topology Seminar
\cventry{Nov 2021}{MIT}{}{Cambridge, MA (\textbf{in person})}{}{}{} % CSAIL talk
\cventry{Nov 2021}{Autodesk}{}{(virtual)}{}{}
\cventry{Nov 2021}{Online Seminar Geometric Analysis}{}{(virtual)}{}{}
\cventry{Oct 2021}{Toronto Geometry Colloquium}{}{Toronto, ON (virtual)}{}{}
\cventry{Apr 2021}{UCSD (CSE)}{}{San Diego, CA (virtual)}{}{}
\cventry{Jan 2021}{UCSD (CCoM)}{}{San Diego, CA (virtual)}{}{}
\cventry{Dec 2020}{CMU}{}{Pittsburgh, PA (virtual)}{}{}
\cventry{May 2020}{GAMES Webinar}{}{(virtual)}{}{}
\cventry{Nov 2019}{College of the Holy Cross}{}{Worcester, MA (virtual)}{}{}
\cventry{Sep 2019}{Inria Grenoble-Rh\^one-Alpes}{}{Grenoble, France}{}{}
\cventry{Aug 2019}{ETH Z\"urich}{}{Z\"urich, Switzerland}{}{}

\subsection{PhD students\ seminars}
\cventry{Aug 2019}{EPFL}{}{Lausanne, Switzerland}{}{} % Snow and Avalanche Simulation Laboratory weekly seminars
\cventry{Nov 2018}{UCLA}{}{Los Angeles, CA}{}{}

\section{Services}
\cventry{2021-present}{External reviewer}{}{}{}{ACM SIGGRAPH, ACM SIGGRAPH Asia, Eurographics}
\cventry{2021}{Research project mentor}{Summer Geometry Institute}{(virtual)}{}{Design project advise undergrad researchers about minimal surfaces using both Lagrangian and Eulerian representations.}
\cventry{2018-2020}{President}{Mathematics Graduate Student Organization, UCLA}{}{}{Coordinate social and academic events and liaise with math faculty and administration representing the math graduate students. }
\cventry{2017-2020}{Math Dept Representative}{Mathematical and Physical Sciences Student Council, UCLA}{}{}{Student rights advocacy and cross-departmental social events planning.}
% \cventry{2015-2020}{Volunteer}{AWiSE STEM Day}{}{}{}
%{Present interactive math booth in annual science fair for middle school girls to encourage them to pursue career in STEM. }
% \cventry{2017-2020}{Volunteer}{Explore Your Universe, UCLA}{}{}{}
%{Present interactive math booth in annual science accessible for all local communities. }
\cventry{2016-2018}{Cheif Organizer}{Women in Math, UCLA}{}{}{Organize social and volunteering events and advocate for women in math dept. }
\cventry{2017}{Creator}{Women in Math Mentorship Program, UCLA}{}{}{Secure fundings, coordinate regular mixers for undergraduate and graduate fellows to increase connection, awareness and mentorship.}
\cventry{2016-2018}{Fellow Mentor}{California Teach, UCLA}{}{}{}%{Mentor Math and Statistics undergraduate students and give academic and career advice.}
\cventry{2012-2013}{Vice President}{Lambda Club, National Taiwan University}{}{}{}%{Organized activities and strengthened community connections; revived the club from 3 people to a group of 30+.}


\section{Skills}
\cvline{Languages}{English and Mandarin Chinese - bilingual proficiency.}{}
\cvline{Programming}{C++, lua, MATLAB, vim, bash, zsh, \LaTeX}
\cvline{Tools}{Houdini, HDK, git, gdb, valgrind, Eigen, tbb, CVX}
\cvline{Mathematics}{Optimization, differential equations, scientific computing, numerical linear algebra.}
\cvline{Hobbies}{Rock climbing, hiking, cooking}


\end{document}
