\documentclass[11pt,a4paper,unicode]{moderncv}

\moderncvtheme{classic}
\usepackage[utf8]{inputenc}

\usepackage[scale=.86]{geometry}          % smaller number -> text takes more space
\AtBeginDocument{\recomputelengths}

% The following lines include both bibentry and hyperref packages while resolving the clash
% See https://tex.stackexchange.com/questions/65348/clash-between-bibentry-and-hyperref-with-bibstyle-elsart-harv
\usepackage{bibentry} % using BibTeX for publication list
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage[unicode]{hyperref} % hyperlinks
\makeatletter\let\@bibitem\saved@bibitem\makeatother

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Stephanie}
\familyname{Wang}
% \address{University of California, San Diego}{Department of Computer Science and Engineering}
\email{evast@g.ucla.edu}
\homepage{https://stephaniewang.page/}

\nopagenumbers{}                    


\begin{document}
\maketitle

\section{Education}
%\cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
\cventry{2014-2020}{Ph.D. in Mathematics}{UCLA}{}{Dissertation advisor: Prof. Joseph Teran}{}
\cventry{2014-2016}{M.S. in Mathematics}{UCLA}{}{}{}
\cventry{2009-2013}{B.S. in Mathematics}{National Taiwan University}{}{\textit{magna cum laude}}
{}


\section{Research Experience}
\cventry{2020-present}{Postdoc -- under Prof. Albert Chern}{UCSD}{}{San Diego, CA}{
Geometry processing, physical simulation, inverse rendering, and geometry learning with an emphasis in mathematical theory. Mentored students: 
    \href{https://sinabiz.github.io/}{Mohammad Sina Nabizadeh} {\small(CSE PhD student)},
    \href{https://www.linkedin.com/in/shiyang-jia-a4aa6b174}{Shiyang Jia} {\small(CSE PhD student)},
    \href{https://chadmckell.com/}{Chad McKell} {\small(Music PhD student)}.
}
\cventry{2019-2020}{Ph.D. Study -- under Prof. Wilfrid Gangbo}{UCLA}{}{Los Angeles, CA}{Regularity theory for minimizers of polyconvex functionals related to Navier-Stokes equation. }
\cventry{2019 summer}{Summer Exchange -- under Prof. Johan Gaume}{EPFL}{}{Lausanne, Switzerland}
{Physical simulation, post-processing, and data analysis of snow and tire interaction using C++ and Python programming; general consultation at the Snow and Avalanche Simulation Laboratory. }
\cventry{2016-2019}{Ph.D. Study -- under Prof. Joseph Teran}{UCLA}{}{Los Angeles, CA}
{Physical simulation of various materials using C++ programming, convex and nonconvex optimizations, numerical PDEs, numerical linear algebra, and multithreading. }
\cventry{2013-2014}{Research Assistantship -- under Prof. Wen-Wei Lin}{NCTU}{}{Hsinchu, Taiwan}{Generalized eigenvalue problems using MATLAB programming.}

\section{Industry Experience}
\cventry{2018 summer}{Technology Intern}{Walt Disney Animation Studio}{}{Burbank, CA}
{R\&D for pioneering simulation technology in animated feature film, teaming with FX artists, numerical analysis, continuum mechanics, C++, HDK.}

\section{Teaching Experience}
% \cventry{2020-present}{Postdoc}{UCSD Computer Science and Engineering}{}{San Diego, CA}{}
\cventry{2020}{Assistant Adjunct Professor}{UCLA Math Dept}{}{Los Angeles, CA (virtual)}
{Taught remote classes for upper and lower division undergratuate courses: Machine Learning (Math156) and Calculus of Several Variables (Math32A).}
\cventry{2019 spring}{Graduate Student Instructor}{UCLA Math Dept}{}{Los Angeles, CA}
{Taught course: Linear Algebra and Applications (Math33A).}
\cventry{2015-2020}{Teaching Assistant}{UCLA Math Dept}{}{Los Angeles, CA}
{Led discussion sessions and graded homework/exams for 11 undergraduate and graduate level courses: linear algebra and introduction to mathematical proofs (Math 115A), undergrad- and grad-level numerical methods (Math 151B, 269A), introductory, intermediate, and advanced C++ programming (PIC 10A, 10B, 10C).}
% \cventry{2014 summer}{Course Organizer}{2014 Formosan Summer School on Logic, Language, and Computation}{}{}{}


\section{Awards and Prizes}
\cventry{May 2022}{Rising Stars in Computer Graphics Research}{WiGRAPH}{}{}{}
\cventry{Jul 2019}{Best Paper Award}{ACM SIGGRAPH/Eurographics Symposium on Computer Animation}{}{}{}
\cventry{Sep 2014}{Eugene V. Cota-Robles Fellowship}{UCLA}{}{}{}
\cventry{Jun 2013}{Dean's Award, College of Science}{National Taiwan University}{}{}{}
\cventry{Aug 2012}{Bronze Medal, Applied and Computational Mathematics}{S.T. Yau College Student Mathematics Contest}{}{}{}

% \section{Preprints}
% \cvline{2022}{
%     \textbf{DeepCurrents: Learning Implicit Representations of Shapes with Boundaries}
%     \small\newline David Palmer, Dmitriy Smirnov, \underline{Stephanie Wang}, Albert Chern, Justin Solomon
%     \newline {CVPR 2022 (accepted)}
%     \href{https://arxiv.org/abs/2111.09383}{(arXiv)}
% }
% \cvline{Nov 2021}{D. Palmer, D. Smirnov, \mathbf{S. Wang}, A. Chern, J. Solomon, \textit{DeepCurrents: Learning Implicit Representations of Shapes with Boundaries}. \href{https://arxiv.org/abs/2111.09383}{(arXiv link)}}
% \cvline{Aug 2019}{J. Carlen, J. Pont, C. Mentus, S. Chang, \underline{S. Wang}, M. Porter, \textit{Role Detection in Bicycle-Sharing Networks Using Multilayer Stochastic Block Models}. \href{https://arxiv.org/abs/1908.09440}{(arXiv link)}}

\section{Publications}
% \nobibliography{publications}
% \bibliographystyle{unsrt}
% \begin{enumerate}
%     \item \bibentry{Blatny:2021}
%     \item \bibentry{Wang:2021}
%     \item \bibentry{Wang:2020}
%     \item \bibentry{Ding:2019}
%     \item \bibentry{Han:2019}
%     \item \bibentry{Wang:2019}
% \end{enumerate}
\cvline{2022}{
    \textbf{Covector Fluids}
    \small\newline Mohammad Sina Nabizadeh, \underline{Stephanie Wang}, Ravi Ramamoorthi, Albert Chern
    \newline {ACM Transactions on Graphics (SIGGRAPH 2022)} 
    \href{https://dl.acm.org/doi/10.1145/3528223.3530120}{(ACM Digital Library)}.
}
\cvline{2022}{
    \textbf{DeepCurrents: Learning Implicit Representations of Shapes with Boundaries}
    \small\newline David Palmer, Dmitriy Smirnov, \underline{Stephanie Wang}, Albert Chern, Justin Solomon
    \newline {Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}
    \href{https://arxiv.org/abs/2111.09383https://openaccess.thecvf.com/content/CVPR2022/papers/Palmer_DeepCurrents_Learning_Implicit_Representations_of_Shapes_With_Boundaries_CVPR_2022_paper.pdf}{(CVF Open Access)}
}
\cvline{2022}{
    \textbf{Role Detection in Bicycle-Sharing Networks Using Multilayer Stochastic Block Models}
    \small\newline Jane Carlen, Jaume de Dios Pont, Cassidy Mentus, Shyr-Shea Chang, \underline{Stephanie Wang}, Mason A. Porter
    \newline {Network Science}
    \href{https://www.cambridge.org/core/journals/network-science/article/role-detection-in-bicyclesharing-networks-using-multilayer-stochastic-block-models/5D73728650C5C3E2DB9455FCDF46F0E2}{(Cambridge Core)}
}
\cvline{2021}{
    \textbf{Computing minimal surfaces with differential forms}
    \small\newline \underline{Stephanie Wang} and Albert Chern
    \newline {ACM Transactions on Graphics (SIGGRAPH 2021)} 
    \href{https://dl.acm.org/doi/10.1145/3450626.3459781}{(ACM Digital Library)}.
}
% \cvline{Aug 2021}{\underline{Stephanie Wang} and Albert Chern, \textit{Computing minimal surfaces with differential forms}, ACM Transactions on Graphics (SIGGRAPH 2021). \href{https://dl.acm.org/doi/10.1145/3450626.3459781}{(ACM Digital Library)}.}
\cvline{2021}{
    \textbf{Computational micromechanics of porous brittle solids}
    \small\newline Lars Blatny, Henning Löwe, \underline{Stephanie Wang}, Johan Gaume
    \newline {Computers and Geotechnics} 
    \href{https://www.sciencedirect.com/science/article/pii/S0266352X21002822}{(ScienceDirect)}
}
% \cvline{Sep 2021}{L. Blatny, H. Löwe, \textbf{S. Wang}, J. Gaume, \textit{Computational micromechanics of porous brittle solids}, Computers and Geotechnics. \href{https://www.sciencedirect.com/science/article/pii/S0266352X21002822}{(ScienceDirect)}}
\cvline{2020}{
    \textbf{A Material Point Method for Elastoplasticity with Ductile Fracture and Frictional Contact}
    \small\newline \underline{Stephanie Wang}
    \newline UCLA Doctoral Dissertation 
    \href{https://www.proquest.com/docview/2389768700?pq-origsite=gscholar&fromopenview=true}{(ProQuest)}
}
% \cvline{Mar 2020}{\underline{Stephanie Wang}, A Material Point Method for Elastoplasticity with Ductile Fracture and Frictional Contact, UCLA Doctoral Dissertation, \href{https://www.proquest.com/docview/2389768700?pq-origsite=gscholar&fromopenview=true}{ProQuest}.}
\cvline{2019}{
    \textbf{A thermomechanical material point method for baking and cooking}
    \small\newline Mengyuan Ding, Xuchen Han, \underline{Stephanie Wang}, Theodore F. Gast, Joseph M. Teran
    \newline ACM Transactions on Graphics (SIGGRAPH Asia 2019) 
    \href{https://dl.acm.org/doi/10.1145/3355089.3356537}{(ACM Digital Library)}
}
% \cvline{Nov 2019}{M. Ding, X. Han, \underline{S. Wang}, T. Gast, J. Teran, A thermomechanical material point method for baking and cooking, ACM Transactions on Graphics (SIGGRAPH Asia 2019), \href{https://dl.acm.org/doi/10.1145/3355089.3356537}{ACM Digital Library}.}
\cvline{2019}{
    \textbf{A Hybrid Material Point Method for Frictional Contact with Diverse Materials}
    \small\newline Xuchen Han, Theodore F. Gast, Qi Guo, \underline{Stephanie Wang}, Chenfanfi Jiang, Joseph M. Teran
    \newline Proceedings of the ACM on Computer Graphics and Interactive Techniques (SCA 2019) 
    \href{https://dl.acm.org/doi/10.1145/3340258}{(ACM Digital Library)} 
}
% \cvline{Jul 2019}{X. Han, T. Gast, Q. Guo, \underline{S. Wang}, C. Jiang, J. Teran, A Hybrid Material Point Method for Frictional Contact with Diverse Materials, Proc ACM on Computer Graphics and Interactive Techniques (SCA 2019), \href{https://dl.acm.org/doi/10.1145/3340258}{ACM Digital Library}. }
\cvline{2019}{
    \textbf{Simulation and Visualization of Ductile Fracture with the Material Point Method}
    \small\newline \underline{Stephanie Wang}, Mengyuan Ding, Theodore F. Gast, Leyi Zhu, Steven Gagniere, Chenfanfu Jiang, Joseph M. Teran
    \newline Proceedings of the ACM on Computer Graphics and Interactive Techniques (SCA 2019 Best Paper) 
    \href{https://dl.acm.org/doi/10.1145/3340259}{(ACM Digital Library)}
}
% \cvline{Jul 2019}{\underline{S. Wang}, M. Ding, T. Gast, L. Zhu, S. Gagniere, C. Jiang, J. Teran, Simulation and Visualization of Ductile Fracture with the Material Point Method, Proc ACM on Computer Graphics and Interactive Techniques (SCA 2019 Best Paper), \href{https://dl.acm.org/doi/10.1145/3340259}{ACM Digital Library}.}

\section{Invited talks}
% \cventry[spacing]{years}{degree/job title}{institution/employer}{localization}{optionnal: grade/...}{optional: comment/job description}
\subsection{Conferences and workshops}
\cventry{Sep 2021}{Geometry Workshop in Obergurgl}{}{Obergurgl, Austria}{}{}
\cventry{Aug 2021}{SIGGRAPH}{}{(virtual)}{}{}
\cventry{Aug 2019}{SCA}{}{Los Angeles, CA}{}{}

\subsection{Seminars at research institutions}
\cventry{Feb 2022}{NCSU}{}{Raleigh, NC (virtual)}{}{}{} % Geometry and Topology Seminar
\cventry{Nov 2021}{MIT}{}{Cambridge, MA}{}{}{} % CSAIL talk
\cventry{Nov 2021}{Autodesk}{}{(virtual)}{}{}
\cventry{Nov 2021}{Online Seminar Geometric Analysis}{}{(virtual)}{}{}
\cventry{Oct 2021}{Toronto Geometry Colloquium}{}{Toronto, ON (virtual)}{}{}
\cventry{Apr 2021}{UCSD (CSE)}{}{San Diego, CA (virtual)}{}{}
\cventry{Jan 2021}{UCSD (CCoM)}{}{San Diego, CA (virtual)}{}{}
\cventry{Dec 2020}{CMU}{}{Pittsburgh, PA (virtual)}{}{}
\cventry{May 2020}{GAMES Webinar}{}{(virtual)}{}{}
\cventry{Nov 2019}{College of the Holy Cross}{}{Worcester, MA (virtual)}{}{}
\cventry{Sep 2019}{Inria Grenoble-Rh\^one-Alpes}{}{Grenoble, France}{}{}
\cventry{Aug 2019}{ETH Z\"urich}{}{Z\"urich, Switzerland}{}{}

\subsection{PhD student seminars}
\cventry{Aug 2019}{EPFL}{}{Lausanne, Switzerland}{}{} % Snow and Avalanche Simulation Laboratory weekly seminars
\cventry{Nov 2018}{UCLA}{}{Los Angeles, CA}{}{}

\section{Services}
\cventry{2021-present}{External reviewer}{ACM SIGGRAPH, SIGGRAPH Asia, Eurographics}{}{}{Reviewed technical papers in areas including geometry processing, physical simulation, and scientific computing.}
\cventry{2021}{Research project mentor}{Summer Geometry Institute}{}{}{Designed a research project and advised undergraduate fellows on minimal surfaces using both Lagrangian and Eulerian representations.}
\cventry{2018-2020}{President}{Mathematics Graduate Student Organization, UCLA}{}{}{Coordinated social events and PhD student seminars and liaised with faculties and administration for math graduate students. }
\cventry{2017-2020}{Math Dept Representative}{Mathematical and Physical Sciences Student Council, UCLA}{}{}{Advocated for student rights in campus-level organizations and organized cross-departmental social events. }
\cventry{2015-2020}{Volunteer}{AWiSE STEM Day}{}{}{Presented interactive math booth in annual science fair designated for middle school girls. }
\cventry{2017-2020}{Volunteer}{Explore Your Universe, UCLA}{}{}{Presented interactive math booth in annual science fair accessible for all local communities. }
\cventry{2016-2018}{Chief Organizer}{Women in Math, UCLA}{}{}{Organized social and volunteering events and generally advocated for women in math dept. }
\cventry{2017}{Creator}{Women in Math Mentorship Program, UCLA}{}{}{Secured funding and coordinated regular mixers for undergraduate and graduate fellows to increase connection, awareness, and mentorship.}
\cventry{2016-2018}{Fellow Mentor}{California Teach, UCLA}{}{}{Mentored Math and Statistics undergraduate students from underrepresented demographics and gave academic and career advice. }
\cventry{2012-2013}{Vice President}{Lambda Club, National Taiwan University}{}{}{Organized events and grew the community from 3 people to 30+ during my service. }


\section{Skills}
\cvline{Languages}{English and Mandarin Chinese - bilingual proficiency.}{}
\cvline{Programming}{C++, lua, MATLAB, vim, bash, zsh, \LaTeX}
\cvline{Tools}{Houdini, HDK, git, gdb, valgrind, Eigen, tbb, CVX}
\cvline{Mathematics}{Optimization, differential geometry, numerical and theoretical PDEs, scientific computing, numerical linear algebra.}
\cvline{Hobbies}{Rock climbing, hiking, cooking}


\end{document}
